Visualization of [fulle name] Fractional Integrals

### 2019-04-26 fractional/CMJ style files/article-template.tex
added a new paragraph

If we set the value of $\alpha$ to $\frac{4}{5}$, but we do not fix the value of $t$ then Eq.~\eqref{eq:ex1} reduces to:
\begin{equation}
\int_{a_{t}^{\frac{4}{5}}(y)}^{b_{t}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
\end{equation}
If we evaluate the above integral we obtain the area of the region $R_{t}^{\frac{4}{5}}$. The region $R_{t}^{\frac{4}{5}}$ is the region bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\frac{4}{5}}(y)$.
Note that $R_{t}^{\frac{4}{5}}$ is a function of $t$. The regions $\mathsf{R}^{\frac{4}{5}}$ are depicted in the rightmost panel of Fig\textbf{??}.

>>>>

If we set the value of $\alpha$ to $\frac{4}{5}$, but we do not fix the value of $t$ then Eq.~\eqref{eq:ex1} reduces to:
\begin{equation}
\int_{a_{t}^{\frac{4}{5}}(y)}^{b_{t}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
\end{equation}
If we evaluate the above integral we obtain the area of the region $R_{t}^{\frac{4}{5}}$. The region $R_{t}^{\frac{4}{5}}$ is the region bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\frac{4}{5}}(y)$.
Note that $R_{t}^{\frac{4}{5}}$ is a function of $t$. The regions contained in the set $\mathsf{R}^{\frac{4}{5}}$ are depicted in the rightmost panel of Fig\textbf{??}. Let $\mathsf{B}^{\frac{4}{5}}$ contain the right 
edges of the regions contained in the set $\mathsf{R}^{\frac{4}{5}}$. The edges in $\mathsf{B}^{\frac{4}{5}}$ are depicted using different shades of gray. The edges that are associated 
with larger values of $t$ are depicted using lighter shades of gray than those that are associated with smaller values of $t$. Note that b and b are not equal, i.e. altering $t$ will alter 
the shape of the integration strip used  . Changing the value of $t$ alters the shape of the non-rectangular integration strip which is needed

limit alters the
shape of the infinitesimal we need to use.

The shade with which the aformentioned edges are depicted becomes lighter as the value of $t$ increases.
